---
title: "Untitled"
output: pdf_document
date: "2024-08-28"
---

```{r}
library(tidyverse)
library(terra)
library(sf)
```

# Test Run 1 (Regular)

```{r}
successionLog <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/LANDIS Outputs/Small Landscape/Test 1/NECN-succession-log.csv")

# Carbon
carbonDf <- successionLog %>% select(Time, SOMTC, C_SOM1surf, C_SOM1soil, C_SOM2, C_SOM3) %>% 
  pivot_longer(cols = "SOMTC":"C_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(carbonDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1\nDecaySoil = 1\nDecaySOM2 = 0.2\nDecaySOM3 = 0.0000001\nDenitrification = 0.013\nNSlope = 0.006\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("SOMTC" = "red", "C_SOM1surf" = "cornflowerblue", "C_SOM1soil" = "darkorchid", "C_SOM2" = "darkorange", "C_SOM3" = "darkgreen"))

# Nitrogen
nitrogenDf <- successionLog %>% select(Time, TotalSoilN, N_SOM1surf, N_SOM1soil, N_SOM2, N_SOM3) %>% 
  pivot_longer(cols = "TotalSoilN":"N_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(nitrogenDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1\nDecaySoil = 1\nDecaySOM2 = 0.2\nDecaySOM3 = 0.0000001\nDenitrification = 0.013\nNSlope = 0.006\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("TotalSoilN" = "red", "N_SOM1surf" = "cornflowerblue", "N_SOM1soil" = "darkorchid", "N_SOM2" = "darkorange", "N_SOM3" = "darkgreen"))

# Ratio
ratioDf <- rbind(carbonDf, nitrogenDf) %>%
  pivot_wider(names_from = "Pool", values_from = "g_m2") %>%
  mutate(Total = SOMTC / TotalSoilN,
         Surf = C_SOM1surf / N_SOM1surf,
         Soil = C_SOM1soil / N_SOM1soil,
         SOM2 = C_SOM2 / N_SOM2,
         SOM3 = C_SOM3 / N_SOM3) %>%
  select(Time, Total, Surf, Soil, SOM2, SOM3) %>%
  pivot_longer(cols = "Total":"SOM3", names_to = "Pool", values_to = "C:N Ratio")

ggplot(ratioDf, aes(x = Time, y = `C:N Ratio`, col = Pool)) +
  geom_line(size  = 1) +
  theme_classic() +
  ylim(0,80) +
  annotate("text", x = 31, y = Inf, label = "DecaySurf = 1\nDecaySoil = 1\nDecaySOM2 = 0.2\nDecaySOM3 = 0.0000001\nDenitrification = 0.013\nNSlope = 0.006\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  geom_hline(yintercept = 5, linetype = "dashed", col = "blue") +
  geom_hline(yintercept = 10, linetype = "dashed") +
  scale_color_manual(values = c("Total" = "red", "Surf" = "cornflowerblue", "Soil" = "darkorchid", "SOM2" = "darkorange", "SOM3" = "darkgreen"))

```

# Test Run 2 (SOM3C * 4)

```{r}
successionLog <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/LANDIS Outputs/Small Landscape/Test 2/NECN-succession-log.csv")

# Carbon
carbonDf <- successionLog %>% select(Time, SOMTC, C_SOM1surf, C_SOM1soil, C_SOM2, C_SOM3) %>% 
  pivot_longer(cols = "SOMTC":"C_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(carbonDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1\nDecaySoil = 1\nDecaySOM2 = 0.2\nDecaySOM3 = 0.0000001\nDenitrification = 0.013\nNSlope = 0.006\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("SOMTC" = "red", "C_SOM1surf" = "cornflowerblue", "C_SOM1soil" = "darkorchid", "C_SOM2" = "darkorange", "C_SOM3" = "darkgreen"))

# Nitrogen
nitrogenDf <- successionLog %>% select(Time, TotalSoilN, N_SOM1surf, N_SOM1soil, N_SOM2, N_SOM3) %>% 
  pivot_longer(cols = "TotalSoilN":"N_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(nitrogenDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1\nDecaySoil = 1\nDecaySOM2 = 0.2\nDecaySOM3 = 0.0000001\nDenitrification = 0.013\nNSlope = 0.006\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("TotalSoilN" = "red", "N_SOM1surf" = "cornflowerblue", "N_SOM1soil" = "darkorchid", "N_SOM2" = "darkorange", "N_SOM3" = "darkgreen"))

# Ratio
ratioDf <- rbind(carbonDf, nitrogenDf) %>%
  pivot_wider(names_from = "Pool", values_from = "g_m2") %>%
  mutate(Total = SOMTC / TotalSoilN,
         Surf = C_SOM1surf / N_SOM1surf,
         Soil = C_SOM1soil / N_SOM1soil,
         SOM2 = C_SOM2 / N_SOM2,
         SOM3 = C_SOM3 / N_SOM3) %>%
  select(Time, Total, Surf, Soil, SOM2, SOM3) %>%
  pivot_longer(cols = "Total":"SOM3", names_to = "Pool", values_to = "C:N Ratio")

ggplot(ratioDf, aes(x = Time, y = `C:N Ratio`, col = Pool)) +
  geom_line(size  = 1) +
  theme_classic() +
  ylim(0,80) +
  annotate("text", x = 31, y = Inf, label = "DecaySurf = 1\nDecaySoil = 1\nDecaySOM2 = 0.2\nDecaySOM3 = 0.0000001\nDenitrification = 0.013\nNSlope = 0.006\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  geom_hline(yintercept = 5, linetype = "dashed", col = "blue") +
  geom_hline(yintercept = 10, linetype = "dashed") +
  scale_color_manual(values = c("Total" = "red", "Surf" = "cornflowerblue", "Soil" = "darkorchid", "SOM2" = "darkorange", "SOM3" = "darkgreen"))

```

# Test Run 3 (Regular, Decay SOM1surf = 1.3)

```{r}
successionLog <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/LANDIS Outputs/Small Landscape/Test 3/NECN-succession-log.csv")

# Carbon
carbonDf <- successionLog %>% select(Time, SOMTC, C_SOM1surf, C_SOM1soil, C_SOM2, C_SOM3) %>% 
  pivot_longer(cols = "SOMTC":"C_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(carbonDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1\nDecaySoil = 1\nDecaySOM2 = 0.2\nDecaySOM3 = 0.0000001\nDenitrification = 0.013\nNSlope = 0.006\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("SOMTC" = "red", "C_SOM1surf" = "cornflowerblue", "C_SOM1soil" = "darkorchid", "C_SOM2" = "darkorange", "C_SOM3" = "darkgreen"))

# Nitrogen
nitrogenDf <- successionLog %>% select(Time, TotalSoilN, N_SOM1surf, N_SOM1soil, N_SOM2, N_SOM3) %>% 
  pivot_longer(cols = "TotalSoilN":"N_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(nitrogenDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1\nDecaySoil = 1\nDecaySOM2 = 0.2\nDecaySOM3 = 0.0000001\nDenitrification = 0.013\nNSlope = 0.006\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("TotalSoilN" = "red", "N_SOM1surf" = "cornflowerblue", "N_SOM1soil" = "darkorchid", "N_SOM2" = "darkorange", "N_SOM3" = "darkgreen"))

# Ratio
ratioDf <- rbind(carbonDf, nitrogenDf) %>%
  pivot_wider(names_from = "Pool", values_from = "g_m2") %>%
  mutate(Total = SOMTC / TotalSoilN,
         Surf = C_SOM1surf / N_SOM1surf,
         Soil = C_SOM1soil / N_SOM1soil,
         SOM2 = C_SOM2 / N_SOM2,
         SOM3 = C_SOM3 / N_SOM3) %>%
  select(Time, Total, Surf, Soil, SOM2, SOM3) %>%
  pivot_longer(cols = "Total":"SOM3", names_to = "Pool", values_to = "C:N Ratio")

ggplot(ratioDf, aes(x = Time, y = `C:N Ratio`, col = Pool)) +
  geom_line(size  = 1) +
  theme_classic() +
  ylim(0,80) +
  annotate("text", x = 31, y = Inf, label = "DecaySurf = 1.3\nDecaySoil = 1\nDecaySOM2 = 0.2\nDecaySOM3 = 0.0000001\nDenitrification = 0.013\nNSlope = 0.006\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  geom_hline(yintercept = 5, linetype = "dashed", col = "blue") +
  geom_hline(yintercept = 10, linetype = "dashed") +
  scale_color_manual(values = c("Total" = "red", "Surf" = "cornflowerblue", "Soil" = "darkorchid", "SOM2" = "darkorange", "SOM3" = "darkgreen"))

```

# Test Run 4 (Decay SOM1surf = 1.3, Deadwood and roots / 2)

```{r}
successionLog <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/LANDIS Outputs/Small Landscape/Test 4/NECN-succession-log.csv")

# Carbon
carbonDf <- successionLog %>% select(Time, SOMTC, C_SOM1surf, C_SOM1soil, C_SOM2, C_SOM3) %>% 
  pivot_longer(cols = "SOMTC":"C_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(carbonDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1\nDecaySoil = 1\nDecaySOM2 = 0.2\nDecaySOM3 = 0.0000001\nDenitrification = 0.013\nNSlope = 0.006\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("SOMTC" = "red", "C_SOM1surf" = "cornflowerblue", "C_SOM1soil" = "darkorchid", "C_SOM2" = "darkorange", "C_SOM3" = "darkgreen"))

# Nitrogen
nitrogenDf <- successionLog %>% select(Time, TotalSoilN, N_SOM1surf, N_SOM1soil, N_SOM2, N_SOM3) %>% 
  pivot_longer(cols = "TotalSoilN":"N_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(nitrogenDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1\nDecaySoil = 1\nDecaySOM2 = 0.2\nDecaySOM3 = 0.0000001\nDenitrification = 0.013\nNSlope = 0.006\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("TotalSoilN" = "red", "N_SOM1surf" = "cornflowerblue", "N_SOM1soil" = "darkorchid", "N_SOM2" = "darkorange", "N_SOM3" = "darkgreen"))

# Ratio
ratioDf <- rbind(carbonDf, nitrogenDf) %>%
  pivot_wider(names_from = "Pool", values_from = "g_m2") %>%
  mutate(Total = SOMTC / TotalSoilN,
         Surf = C_SOM1surf / N_SOM1surf,
         Soil = C_SOM1soil / N_SOM1soil,
         SOM2 = C_SOM2 / N_SOM2,
         SOM3 = C_SOM3 / N_SOM3) %>%
  select(Time, Total, Surf, Soil, SOM2, SOM3) %>%
  pivot_longer(cols = "Total":"SOM3", names_to = "Pool", values_to = "C:N Ratio")

ggplot(ratioDf, aes(x = Time, y = `C:N Ratio`, col = Pool)) +
  geom_line(size  = 1) +
  theme_classic() +
  ylim(0,80) +
  annotate("text", x = 31, y = Inf, label = "DecaySurf = 1.3\nDecaySoil = 1\nDecaySOM2 = 0.2\nDecaySOM3 = 0.0000001\nDenitrification = 0.013\nNSlope = 0.006\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  geom_hline(yintercept = 5, linetype = "dashed", col = "blue") +
  geom_hline(yintercept = 10, linetype = "dashed") +
  scale_color_manual(values = c("Total" = "red", "Surf" = "cornflowerblue", "Soil" = "darkorchid", "SOM2" = "darkorange", "SOM3" = "darkgreen"))

```

# Test Run 5 (Decay SOM1surf = 1.3, Deadwood and roots * 0.001)

```{r}
successionLog <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/LANDIS Outputs/Small Landscape/Test 5/NECN-succession-log.csv")

# Carbon
carbonDf <- successionLog %>% select(Time, SOMTC, C_SOM1surf, C_SOM1soil, C_SOM2, C_SOM3) %>% 
  pivot_longer(cols = "SOMTC":"C_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(carbonDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.3\nDecaySoil = 1\nDecaySOM2 = 0.2\nDecaySOM3 = 0.0000001\nDenitrification = 0.013\nNSlope = 0.006\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("SOMTC" = "red", "C_SOM1surf" = "cornflowerblue", "C_SOM1soil" = "darkorchid", "C_SOM2" = "darkorange", "C_SOM3" = "darkgreen"))

# Nitrogen
nitrogenDf <- successionLog %>% select(Time, TotalSoilN, N_SOM1surf, N_SOM1soil, N_SOM2, N_SOM3) %>% 
  pivot_longer(cols = "TotalSoilN":"N_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(nitrogenDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.3\nDecaySoil = 1\nDecaySOM2 = 0.2\nDecaySOM3 = 0.0000001\nDenitrification = 0.013\nNSlope = 0.006\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("TotalSoilN" = "red", "N_SOM1surf" = "cornflowerblue", "N_SOM1soil" = "darkorchid", "N_SOM2" = "darkorange", "N_SOM3" = "darkgreen"))

# Ratio
ratioDf <- rbind(carbonDf, nitrogenDf) %>%
  pivot_wider(names_from = "Pool", values_from = "g_m2") %>%
  mutate(Total = SOMTC / TotalSoilN,
         Surf = C_SOM1surf / N_SOM1surf,
         Soil = C_SOM1soil / N_SOM1soil,
         SOM2 = C_SOM2 / N_SOM2,
         SOM3 = C_SOM3 / N_SOM3) %>%
  select(Time, Total, Surf, Soil, SOM2, SOM3) %>%
  pivot_longer(cols = "Total":"SOM3", names_to = "Pool", values_to = "C:N Ratio")

ggplot(ratioDf, aes(x = Time, y = `C:N Ratio`, col = Pool)) +
  geom_line(size  = 1) +
  theme_classic() +
  ylim(0,80) +
  annotate("text", x = 31, y = Inf, label = "DecaySurf = 1.3\nDecaySoil = 1\nDecaySOM2 = 0.2\nDecaySOM3 = 0.0000001\nDenitrification = 0.013\nNSlope = 0.006\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  geom_hline(yintercept = 5, linetype = "dashed", col = "blue") +
  geom_hline(yintercept = 10, linetype = "dashed") +
  scale_color_manual(values = c("Total" = "red", "Surf" = "cornflowerblue", "Soil" = "darkorchid", "SOM2" = "darkorange", "SOM3" = "darkgreen"))

```

# Test Run 6 (Decay SOM1surf = 1.3, DOM1soil = 2, Deadwood and roots * 0.001)

```{r}
successionLog <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/LANDIS Outputs/Small Landscape/Test 6/NECN-succession-log.csv")

# Carbon
carbonDf <- successionLog %>% select(Time, SOMTC, C_SOM1surf, C_SOM1soil, C_SOM2, C_SOM3) %>% 
  pivot_longer(cols = "SOMTC":"C_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(carbonDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.3\nDecaySoil = 2\nDecaySOM2 = 0.2\nDecaySOM3 = 0.0000001\nDenitrification = 0.013\nNSlope = 0.006\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("SOMTC" = "red", "C_SOM1surf" = "cornflowerblue", "C_SOM1soil" = "darkorchid", "C_SOM2" = "darkorange", "C_SOM3" = "darkgreen"))

# Nitrogen
nitrogenDf <- successionLog %>% select(Time, TotalSoilN, N_SOM1surf, N_SOM1soil, N_SOM2, N_SOM3) %>% 
  pivot_longer(cols = "TotalSoilN":"N_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(nitrogenDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.3\nDecaySoil = 2\nDecaySOM2 = 0.2\nDecaySOM3 = 0.0000001\nDenitrification = 0.013\nNSlope = 0.006\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("TotalSoilN" = "red", "N_SOM1surf" = "cornflowerblue", "N_SOM1soil" = "darkorchid", "N_SOM2" = "darkorange", "N_SOM3" = "darkgreen"))

# Ratio
ratioDf <- rbind(carbonDf, nitrogenDf) %>%
  pivot_wider(names_from = "Pool", values_from = "g_m2") %>%
  mutate(Total = SOMTC / TotalSoilN,
         Surf = C_SOM1surf / N_SOM1surf,
         Soil = C_SOM1soil / N_SOM1soil,
         SOM2 = C_SOM2 / N_SOM2,
         SOM3 = C_SOM3 / N_SOM3) %>%
  select(Time, Total, Surf, Soil, SOM2, SOM3) %>%
  pivot_longer(cols = "Total":"SOM3", names_to = "Pool", values_to = "C:N Ratio")

ggplot(ratioDf, aes(x = Time, y = `C:N Ratio`, col = Pool)) +
  geom_line(size  = 1) +
  theme_classic() +
  ylim(0,80) +
  annotate("text", x = 31, y = Inf, label = "DecaySurf = 1.3\nDecaySoil = 2\nDecaySOM2 = 0.2\nDecaySOM3 = 0.0000001\nDenitrification = 0.013\nNSlope = 0.006\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  geom_hline(yintercept = 5, linetype = "dashed", col = "blue") +
  geom_hline(yintercept = 10, linetype = "dashed") +
  scale_color_manual(values = c("Total" = "red", "Surf" = "cornflowerblue", "Soil" = "darkorchid", "SOM2" = "darkorange", "SOM3" = "darkgreen"))

```

# Test Run 7 (Decay SOM1surf = 1.3, SOM1soil = 2, SOM2 = 0.4, Deadwood and roots * 0.001)

```{r}
successionLog <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/LANDIS Outputs/Small Landscape/Test 7/NECN-succession-log.csv")

# Carbon
carbonDf <- successionLog %>% select(Time, SOMTC, C_SOM1surf, C_SOM1soil, C_SOM2, C_SOM3) %>% 
  pivot_longer(cols = "SOMTC":"C_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(carbonDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.3\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.013\nNSlope = 0.006\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("SOMTC" = "red", "C_SOM1surf" = "cornflowerblue", "C_SOM1soil" = "darkorchid", "C_SOM2" = "darkorange", "C_SOM3" = "darkgreen"))

# Nitrogen
nitrogenDf <- successionLog %>% select(Time, TotalSoilN, N_SOM1surf, N_SOM1soil, N_SOM2, N_SOM3) %>% 
  pivot_longer(cols = "TotalSoilN":"N_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(nitrogenDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.3\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.013\nNSlope = 0.006\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("TotalSoilN" = "red", "N_SOM1surf" = "cornflowerblue", "N_SOM1soil" = "darkorchid", "N_SOM2" = "darkorange", "N_SOM3" = "darkgreen"))

# Ratio
ratioDf <- rbind(carbonDf, nitrogenDf) %>%
  pivot_wider(names_from = "Pool", values_from = "g_m2") %>%
  mutate(Total = SOMTC / TotalSoilN,
         Surf = C_SOM1surf / N_SOM1surf,
         Soil = C_SOM1soil / N_SOM1soil,
         SOM2 = C_SOM2 / N_SOM2,
         SOM3 = C_SOM3 / N_SOM3) %>%
  select(Time, Total, Surf, Soil, SOM2, SOM3) %>%
  pivot_longer(cols = "Total":"SOM3", names_to = "Pool", values_to = "C:N Ratio")

ggplot(ratioDf, aes(x = Time, y = `C:N Ratio`, col = Pool)) +
  geom_line(size  = 1) +
  theme_classic() +
  ylim(0,80) +
  annotate("text", x = 31, y = Inf, label = "DecaySurf = 1.3\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.013\nNSlope = 0.006\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  geom_hline(yintercept = 5, linetype = "dashed", col = "blue") +
  geom_hline(yintercept = 10, linetype = "dashed") +
  scale_color_manual(values = c("Total" = "red", "Surf" = "cornflowerblue", "Soil" = "darkorchid", "SOM2" = "darkorange", "SOM3" = "darkgreen"))

```

# Test Run 8 (Decay SOM1surf = 1.3, SOM1soil = 2, SOM2 = 0.4, Deadwood and roots * 0.001, NSlope = 0.01, DeNitrif = 0.02)

```{r}
successionLog <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/LANDIS Outputs/Small Landscape/Test 8/NECN-succession-log.csv")

# Carbon
carbonDf <- successionLog %>% select(Time, SOMTC, C_SOM1surf, C_SOM1soil, C_SOM2, C_SOM3) %>% 
  pivot_longer(cols = "SOMTC":"C_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(carbonDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.3\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.02\nNSlope = 0.01\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("SOMTC" = "red", "C_SOM1surf" = "cornflowerblue", "C_SOM1soil" = "darkorchid", "C_SOM2" = "darkorange", "C_SOM3" = "darkgreen"))

# Nitrogen
nitrogenDf <- successionLog %>% select(Time, TotalSoilN, N_SOM1surf, N_SOM1soil, N_SOM2, N_SOM3) %>% 
  pivot_longer(cols = "TotalSoilN":"N_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(nitrogenDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.3\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.02\nNSlope = 0.01\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("TotalSoilN" = "red", "N_SOM1surf" = "cornflowerblue", "N_SOM1soil" = "darkorchid", "N_SOM2" = "darkorange", "N_SOM3" = "darkgreen"))

# Ratio
ratioDf <- rbind(carbonDf, nitrogenDf) %>%
  pivot_wider(names_from = "Pool", values_from = "g_m2") %>%
  mutate(Total = SOMTC / TotalSoilN,
         Surf = C_SOM1surf / N_SOM1surf,
         Soil = C_SOM1soil / N_SOM1soil,
         SOM2 = C_SOM2 / N_SOM2,
         SOM3 = C_SOM3 / N_SOM3) %>%
  select(Time, Total, Surf, Soil, SOM2, SOM3) %>%
  pivot_longer(cols = "Total":"SOM3", names_to = "Pool", values_to = "C:N Ratio")

ggplot(ratioDf, aes(x = Time, y = `C:N Ratio`, col = Pool)) +
  geom_line(size  = 1) +
  theme_classic() +
  ylim(0,80) +
  annotate("text", x = 31, y = Inf, label = "DecaySurf = 1.3\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.02\nNSlope = 0.01\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  geom_hline(yintercept = 5, linetype = "dashed", col = "blue") +
  geom_hline(yintercept = 40, linetype = "dashed") +
  scale_color_manual(values = c("Total" = "red", "Surf" = "cornflowerblue", "Soil" = "darkorchid", "SOM2" = "darkorange", "SOM3" = "darkgreen"))

```

# Test Run 9 (Decay SOM1surf = 1.3, SOM1soil = 2, SOM2 = 0.4, Deadwood and roots * 0.001, NSlope = 0.01, DeNitrif = 0.02)
# values(SOM1surfN * 3), values(SOM2N * 3)

```{r}
successionLog <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/LANDIS Outputs/Small Landscape/Test 9/NECN-succession-log.csv")

# Carbon
carbonDf <- successionLog %>% select(Time, SOMTC, C_SOM1surf, C_SOM1soil, C_SOM2, C_SOM3) %>% 
  pivot_longer(cols = "SOMTC":"C_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(carbonDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.3\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.02\nNSlope = 0.01\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("SOMTC" = "red", "C_SOM1surf" = "cornflowerblue", "C_SOM1soil" = "darkorchid", "C_SOM2" = "darkorange", "C_SOM3" = "darkgreen"))

# Nitrogen
nitrogenDf <- successionLog %>% select(Time, TotalSoilN, N_SOM1surf, N_SOM1soil, N_SOM2, N_SOM3) %>% 
  pivot_longer(cols = "TotalSoilN":"N_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(nitrogenDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.3\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.02\nNSlope = 0.01\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("TotalSoilN" = "red", "N_SOM1surf" = "cornflowerblue", "N_SOM1soil" = "darkorchid", "N_SOM2" = "darkorange", "N_SOM3" = "darkgreen"))

# Ratio
ratioDf <- rbind(carbonDf, nitrogenDf) %>%
  pivot_wider(names_from = "Pool", values_from = "g_m2") %>%
  mutate(Total = SOMTC / TotalSoilN,
         Surf = C_SOM1surf / N_SOM1surf,
         Soil = C_SOM1soil / N_SOM1soil,
         SOM2 = C_SOM2 / N_SOM2,
         SOM3 = C_SOM3 / N_SOM3) %>%
  select(Time, Total, Surf, Soil, SOM2, SOM3) %>%
  pivot_longer(cols = "Total":"SOM3", names_to = "Pool", values_to = "C:N Ratio")

ggplot(ratioDf, aes(x = Time, y = `C:N Ratio`, col = Pool)) +
  geom_line(size  = 1) +
  theme_classic() +
  ylim(0,80) +
  annotate("text", x = 31, y = Inf, label = "DecaySurf = 1.3\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.02\nNSlope = 0.01\nNIntercept = 0.28", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  geom_hline(yintercept = 5, linetype = "dashed", col = "blue") +
  geom_hline(yintercept = 10, linetype = "dashed") +
  scale_color_manual(values = c("Total" = "red", "Surf" = "cornflowerblue", "Soil" = "darkorchid", "SOM2" = "darkorange", "SOM3" = "darkgreen"))

```

# Test Run 10 (Decay SOM1surf = 1.3, SOM1soil = 2, SOM2 = 0.4, Deadwood and roots * 0.001, NSlope = 0.01, DeNitrif = 0.05, NIntercept = 0.35)

```{r}
successionLog <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/LANDIS Outputs/Small Landscape/Test 10/NECN-succession-log.csv")

# Carbon
carbonDf <- successionLog %>% select(Time, SOMTC, C_SOM1surf, C_SOM1soil, C_SOM2, C_SOM3) %>% 
  pivot_longer(cols = "SOMTC":"C_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(carbonDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.3\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.35", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("SOMTC" = "red", "C_SOM1surf" = "cornflowerblue", "C_SOM1soil" = "darkorchid", "C_SOM2" = "darkorange", "C_SOM3" = "darkgreen"))

# Nitrogen
nitrogenDf <- successionLog %>% select(Time, TotalSoilN, N_SOM1surf, N_SOM1soil, N_SOM2, N_SOM3) %>% 
  pivot_longer(cols = "TotalSoilN":"N_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(nitrogenDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.3\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.35", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("TotalSoilN" = "red", "N_SOM1surf" = "cornflowerblue", "N_SOM1soil" = "darkorchid", "N_SOM2" = "darkorange", "N_SOM3" = "darkgreen"))

# Ratio
ratioDf <- rbind(carbonDf, nitrogenDf) %>%
  pivot_wider(names_from = "Pool", values_from = "g_m2") %>%
  mutate(Total = SOMTC / TotalSoilN,
         Surf = C_SOM1surf / N_SOM1surf,
         Soil = C_SOM1soil / N_SOM1soil,
         SOM2 = C_SOM2 / N_SOM2,
         SOM3 = C_SOM3 / N_SOM3) %>%
  select(Time, Total, Surf, Soil, SOM2, SOM3) %>%
  pivot_longer(cols = "Total":"SOM3", names_to = "Pool", values_to = "C:N Ratio")

ggplot(ratioDf, aes(x = Time, y = `C:N Ratio`, col = Pool)) +
  geom_line(size  = 1) +
  theme_classic() +
  ylim(0,80) +
  annotate("text", x = 31, y = Inf, label = "DecaySurf = 1.3\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.35", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  geom_hline(yintercept = 5, linetype = "dashed", col = "blue") +
  geom_hline(yintercept = 10, linetype = "dashed") +
  scale_color_manual(values = c("Total" = "red", "Surf" = "cornflowerblue", "Soil" = "darkorchid", "SOM2" = "darkorange", "SOM3" = "darkgreen"))

```

# Test Run 11 (Decay SOM1surf = 1.34, SOM1soil = 2, SOM2 = 0.4, Deadwood and roots * 0.001, NSlope = 0.01, DeNitrif = 0.05, NIntercept = 0.35)

```{r}
successionLog <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/LANDIS Outputs/Small Landscape/Test 11/NECN-succession-log.csv")

# Carbon
carbonDf <- successionLog %>% select(Time, SOMTC, C_SOM1surf, C_SOM1soil, C_SOM2, C_SOM3) %>% 
  pivot_longer(cols = "SOMTC":"C_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(carbonDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.35", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("SOMTC" = "red", "C_SOM1surf" = "cornflowerblue", "C_SOM1soil" = "darkorchid", "C_SOM2" = "darkorange", "C_SOM3" = "darkgreen"))

# Nitrogen
nitrogenDf <- successionLog %>% select(Time, TotalSoilN, N_SOM1surf, N_SOM1soil, N_SOM2, N_SOM3) %>% 
  pivot_longer(cols = "TotalSoilN":"N_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(nitrogenDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.35", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("TotalSoilN" = "red", "N_SOM1surf" = "cornflowerblue", "N_SOM1soil" = "darkorchid", "N_SOM2" = "darkorange", "N_SOM3" = "darkgreen"))

# Ratio
ratioDf <- rbind(carbonDf, nitrogenDf) %>%
  pivot_wider(names_from = "Pool", values_from = "g_m2") %>%
  mutate(Total = SOMTC / TotalSoilN,
         Surf = C_SOM1surf / N_SOM1surf,
         Soil = C_SOM1soil / N_SOM1soil,
         SOM2 = C_SOM2 / N_SOM2,
         SOM3 = C_SOM3 / N_SOM3) %>%
  select(Time, Total, Surf, Soil, SOM2, SOM3) %>%
  pivot_longer(cols = "Total":"SOM3", names_to = "Pool", values_to = "C:N Ratio")

ggplot(ratioDf, aes(x = Time, y = `C:N Ratio`, col = Pool)) +
  geom_line(size  = 1) +
  theme_classic() +
  ylim(0,80) +
  annotate("text", x = 31, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.35", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  geom_hline(yintercept = 5, linetype = "dashed", col = "blue") +
  geom_hline(yintercept = 10, linetype = "dashed") +
  scale_color_manual(values = c("Total" = "red", "Surf" = "cornflowerblue", "Soil" = "darkorchid", "SOM2" = "darkorange", "SOM3" = "darkgreen"))

```

# Test Run 12 (Decay SOM1surf = 1.34, SOM1soil = 2, SOM2 = 0.4, Deadwood and roots * 0.001, NSlope = 0.01, DeNitrif = 0.05, NIntercept = 0.25)

```{r}
successionLog <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/LANDIS Outputs/Small Landscape/Test 12/NECN-succession-log.csv")

# Carbon
carbonDf <- successionLog %>% select(Time, SOMTC, C_SOM1surf, C_SOM1soil, C_SOM2, C_SOM3) %>% 
  pivot_longer(cols = "SOMTC":"C_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(carbonDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("SOMTC" = "red", "C_SOM1surf" = "cornflowerblue", "C_SOM1soil" = "darkorchid", "C_SOM2" = "darkorange", "C_SOM3" = "darkgreen"))

# Nitrogen
nitrogenDf <- successionLog %>% select(Time, TotalSoilN, N_SOM1surf, N_SOM1soil, N_SOM2, N_SOM3) %>% 
  pivot_longer(cols = "TotalSoilN":"N_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(nitrogenDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("TotalSoilN" = "red", "N_SOM1surf" = "cornflowerblue", "N_SOM1soil" = "darkorchid", "N_SOM2" = "darkorange", "N_SOM3" = "darkgreen"))

# Ratio
ratioDf <- rbind(carbonDf, nitrogenDf) %>%
  pivot_wider(names_from = "Pool", values_from = "g_m2") %>%
  mutate(Total = SOMTC / TotalSoilN,
         Surf = C_SOM1surf / N_SOM1surf,
         Soil = C_SOM1soil / N_SOM1soil,
         SOM2 = C_SOM2 / N_SOM2,
         SOM3 = C_SOM3 / N_SOM3) %>%
  select(Time, Total, Surf, Soil, SOM2, SOM3) %>%
  pivot_longer(cols = "Total":"SOM3", names_to = "Pool", values_to = "C:N Ratio")

ggplot(ratioDf, aes(x = Time, y = `C:N Ratio`, col = Pool)) +
  geom_line(size  = 1) +
  theme_classic() +
  ylim(0,80) +
  annotate("text", x = 31, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  geom_hline(yintercept = 5, linetype = "dashed", col = "blue") +
  geom_hline(yintercept = 10, linetype = "dashed") +
  scale_color_manual(values = c("Total" = "red", "Surf" = "cornflowerblue", "Soil" = "darkorchid", "SOM2" = "darkorange", "SOM3" = "darkgreen"))

```

# Test Run 13 (Decay SOM1surf = 1.34, SOM1soil = 2, SOM2 = 0.4, Deadwood and roots * 0.001, NSlope = 0.01, DeNitrif = 0.05, NIntercept = 0.25)
# Future climate test (MRI-CGCM3-RCP85)

```{r}
successionLog <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/LANDIS Outputs/Small Landscape/Test 13/NECN-succession-log.csv")

# Carbon
carbonDf <- successionLog %>% select(Time, SOMTC, C_SOM1surf, C_SOM1soil, C_SOM2, C_SOM3) %>% 
  pivot_longer(cols = "SOMTC":"C_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(carbonDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("SOMTC" = "red", "C_SOM1surf" = "cornflowerblue", "C_SOM1soil" = "darkorchid", "C_SOM2" = "darkorange", "C_SOM3" = "darkgreen"))

# Nitrogen
nitrogenDf <- successionLog %>% select(Time, TotalSoilN, N_SOM1surf, N_SOM1soil, N_SOM2, N_SOM3) %>% 
  pivot_longer(cols = "TotalSoilN":"N_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(nitrogenDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("TotalSoilN" = "red", "N_SOM1surf" = "cornflowerblue", "N_SOM1soil" = "darkorchid", "N_SOM2" = "darkorange", "N_SOM3" = "darkgreen"))

# Ratio
ratioDf <- rbind(carbonDf, nitrogenDf) %>%
  pivot_wider(names_from = "Pool", values_from = "g_m2") %>%
  mutate(Total = SOMTC / TotalSoilN,
         Surf = C_SOM1surf / N_SOM1surf,
         Soil = C_SOM1soil / N_SOM1soil,
         SOM2 = C_SOM2 / N_SOM2,
         SOM3 = C_SOM3 / N_SOM3) %>%
  select(Time, Total, Surf, Soil, SOM2, SOM3) %>%
  pivot_longer(cols = "Total":"SOM3", names_to = "Pool", values_to = "C:N Ratio")

ggplot(ratioDf, aes(x = Time, y = `C:N Ratio`, col = Pool)) +
  geom_line(size  = 1) +
  theme_classic() +
  ylim(0,80) +
  annotate("text", x = 31, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  geom_hline(yintercept = 5, linetype = "dashed", col = "blue") +
  geom_hline(yintercept = 10, linetype = "dashed") +
  scale_color_manual(values = c("Total" = "red", "Surf" = "cornflowerblue", "Soil" = "darkorchid", "SOM2" = "darkorange", "SOM3" = "darkgreen"))

```

# Test Run 14 (Decay SOM1surf = 1.34, SOM1soil = 2, SOM2 = 0.4, Deadwood and roots * 0.001, NSlope = 0.01, DeNitrif = 0.05, NIntercept = 0.25)
# Historical Climate
# SOM1surfC * 0.5, SOM1soilC * 0.5

```{r}
successionLog <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/LANDIS Outputs/Small Landscape/Test 14/NECN-succession-log.csv")

# Carbon
carbonDf <- successionLog %>% select(Time, SOMTC, C_SOM1surf, C_SOM1soil, C_SOM2, C_SOM3) %>% 
  pivot_longer(cols = "SOMTC":"C_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(carbonDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("SOMTC" = "red", "C_SOM1surf" = "cornflowerblue", "C_SOM1soil" = "darkorchid", "C_SOM2" = "darkorange", "C_SOM3" = "darkgreen"))

# Nitrogen
nitrogenDf <- successionLog %>% select(Time, TotalSoilN, N_SOM1surf, N_SOM1soil, N_SOM2, N_SOM3) %>% 
  pivot_longer(cols = "TotalSoilN":"N_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(nitrogenDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("TotalSoilN" = "red", "N_SOM1surf" = "cornflowerblue", "N_SOM1soil" = "darkorchid", "N_SOM2" = "darkorange", "N_SOM3" = "darkgreen"))

# Ratio
ratioDf <- rbind(carbonDf, nitrogenDf) %>%
  pivot_wider(names_from = "Pool", values_from = "g_m2") %>%
  mutate(Total = SOMTC / TotalSoilN,
         Surf = C_SOM1surf / N_SOM1surf,
         Soil = C_SOM1soil / N_SOM1soil,
         SOM2 = C_SOM2 / N_SOM2,
         SOM3 = C_SOM3 / N_SOM3) %>%
  select(Time, Total, Surf, Soil, SOM2, SOM3) %>%
  pivot_longer(cols = "Total":"SOM3", names_to = "Pool", values_to = "C:N Ratio")

ggplot(ratioDf, aes(x = Time, y = `C:N Ratio`, col = Pool)) +
  geom_line(size  = 1) +
  theme_classic() +
  ylim(0,80) +
  annotate("text", x = 31, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  geom_hline(yintercept = 5, linetype = "dashed", col = "blue") +
  geom_hline(yintercept = 10, linetype = "dashed") +
  scale_color_manual(values = c("Total" = "red", "Surf" = "cornflowerblue", "Soil" = "darkorchid", "SOM2" = "darkorange", "SOM3" = "darkgreen"))

```

# Test Run 15 (Decay SOM1surf = 1.34, SOM1soil = 2, SOM2 = 0.4, Deadwood and roots * 0.001, NSlope = 0.01, DeNitrif = 0.05, NIntercept = 0.25)
# SOM1surfN * 0.5, SOM2N * 0.5

```{r}
successionLog <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/LANDIS Outputs/Small Landscape/Test 15/NECN-succession-log.csv")

# Carbon
carbonDf <- successionLog %>% select(Time, SOMTC, C_SOM1surf, C_SOM1soil, C_SOM2, C_SOM3) %>% 
  pivot_longer(cols = "SOMTC":"C_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(carbonDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("SOMTC" = "red", "C_SOM1surf" = "cornflowerblue", "C_SOM1soil" = "darkorchid", "C_SOM2" = "darkorange", "C_SOM3" = "darkgreen"))

# Nitrogen
nitrogenDf <- successionLog %>% select(Time, TotalSoilN, N_SOM1surf, N_SOM1soil, N_SOM2, N_SOM3) %>% 
  pivot_longer(cols = "TotalSoilN":"N_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(nitrogenDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("TotalSoilN" = "red", "N_SOM1surf" = "cornflowerblue", "N_SOM1soil" = "darkorchid", "N_SOM2" = "darkorange", "N_SOM3" = "darkgreen"))

# Ratio
ratioDf <- rbind(carbonDf, nitrogenDf) %>%
  pivot_wider(names_from = "Pool", values_from = "g_m2") %>%
  mutate(Total = SOMTC / TotalSoilN,
         Surf = C_SOM1surf / N_SOM1surf,
         Soil = C_SOM1soil / N_SOM1soil,
         SOM2 = C_SOM2 / N_SOM2,
         SOM3 = C_SOM3 / N_SOM3) %>%
  select(Time, Total, Surf, Soil, SOM2, SOM3) %>%
  pivot_longer(cols = "Total":"SOM3", names_to = "Pool", values_to = "C:N Ratio")

ggplot(ratioDf, aes(x = Time, y = `C:N Ratio`, col = Pool)) +
  geom_line(size  = 1) +
  theme_classic() +
  ylim(0,80) +
  annotate("text", x = 31, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  # geom_hline(yintercept = 5, linetype = "dashed", col = "blue") +
  # geom_hline(yintercept = 10, linetype = "dashed") +
  scale_color_manual(values = c("Total" = "red", "Surf" = "cornflowerblue", "Soil" = "darkorchid", "SOM2" = "darkorange", "SOM3" = "darkgreen"))

```

# Test Run 16 (Decay SOM1surf = 1.34, SOM1soil = 2, SOM2 = 0.4, Deadwood and roots * 0.001, NSlope = 0.01, DeNitrif = 0.05, NIntercept = 0.25)
# SOM1surfN * 0.25, SOM2N * 0.25

```{r}
successionLog <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/LANDIS Outputs/Small Landscape/Test 16/NECN-succession-log.csv")

# Carbon
carbonDf <- successionLog %>% select(Time, SOMTC, C_SOM1surf, C_SOM1soil, C_SOM2, C_SOM3) %>% 
  pivot_longer(cols = "SOMTC":"C_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(carbonDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("SOMTC" = "red", "C_SOM1surf" = "cornflowerblue", "C_SOM1soil" = "darkorchid", "C_SOM2" = "darkorange", "C_SOM3" = "darkgreen"))

# Nitrogen
nitrogenDf <- successionLog %>% select(Time, TotalSoilN, N_SOM1surf, N_SOM1soil, N_SOM2, N_SOM3) %>% 
  pivot_longer(cols = "TotalSoilN":"N_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(nitrogenDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("TotalSoilN" = "red", "N_SOM1surf" = "cornflowerblue", "N_SOM1soil" = "darkorchid", "N_SOM2" = "darkorange", "N_SOM3" = "darkgreen"))

# Ratio
ratioDf <- rbind(carbonDf, nitrogenDf) %>%
  pivot_wider(names_from = "Pool", values_from = "g_m2") %>%
  mutate(Total = SOMTC / TotalSoilN,
         Surf = C_SOM1surf / N_SOM1surf,
         Soil = C_SOM1soil / N_SOM1soil,
         SOM2 = C_SOM2 / N_SOM2,
         SOM3 = C_SOM3 / N_SOM3) %>%
  select(Time, Total, Surf, Soil, SOM2, SOM3) %>%
  pivot_longer(cols = "Total":"SOM3", names_to = "Pool", values_to = "C:N Ratio")

ggplot(ratioDf, aes(x = Time, y = `C:N Ratio`, col = Pool)) +
  geom_line(size  = 1) +
  theme_classic() +
  ylim(0,80) +
  annotate("text", x = 31, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  # geom_hline(yintercept = 5, linetype = "dashed", col = "blue") +
  # geom_hline(yintercept = 10, linetype = "dashed") +
  scale_color_manual(values = c("Total" = "red", "Surf" = "cornflowerblue", "Soil" = "darkorchid", "SOM2" = "darkorange", "SOM3" = "darkgreen"))

```


# Test Run 17 (Decay SOM1surf = 1.34, SOM1soil = 2, SOM2 = 0.4, Deadwood and roots * 0.001, NSlope = 0.01, DeNitrif = 0.05, NIntercept = 0.25)
# SOM1surfN * 0.25, SOM2N * 0.25
# Drainage * 0.5

```{r}
successionLog <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/LANDIS Outputs/Small Landscape/Test 17/NECN-succession-log.csv")

# Carbon
carbonDf <- successionLog %>% select(Time, SOMTC, C_SOM1surf, C_SOM1soil, C_SOM2, C_SOM3) %>% 
  pivot_longer(cols = "SOMTC":"C_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(carbonDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("SOMTC" = "red", "C_SOM1surf" = "cornflowerblue", "C_SOM1soil" = "darkorchid", "C_SOM2" = "darkorange", "C_SOM3" = "darkgreen"))

# Nitrogen
nitrogenDf <- successionLog %>% select(Time, TotalSoilN, N_SOM1surf, N_SOM1soil, N_SOM2, N_SOM3) %>% 
  pivot_longer(cols = "TotalSoilN":"N_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(nitrogenDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("TotalSoilN" = "red", "N_SOM1surf" = "cornflowerblue", "N_SOM1soil" = "darkorchid", "N_SOM2" = "darkorange", "N_SOM3" = "darkgreen"))

# Ratio
ratioDf <- rbind(carbonDf, nitrogenDf) %>%
  pivot_wider(names_from = "Pool", values_from = "g_m2") %>%
  mutate(Total = SOMTC / TotalSoilN,
         Surf = C_SOM1surf / N_SOM1surf,
         Soil = C_SOM1soil / N_SOM1soil,
         SOM2 = C_SOM2 / N_SOM2,
         SOM3 = C_SOM3 / N_SOM3) %>%
  select(Time, Total, Surf, Soil, SOM2, SOM3) %>%
  pivot_longer(cols = "Total":"SOM3", names_to = "Pool", values_to = "C:N Ratio")

ggplot(ratioDf, aes(x = Time, y = `C:N Ratio`, col = Pool)) +
  geom_line(size  = 1) +
  theme_classic() +
  ylim(0,80) +
  annotate("text", x = 31, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  # geom_hline(yintercept = 5, linetype = "dashed", col = "blue") +
  # geom_hline(yintercept = 10, linetype = "dashed") +
  scale_color_manual(values = c("Total" = "red", "Surf" = "cornflowerblue", "Soil" = "darkorchid", "SOM2" = "darkorange", "SOM3" = "darkgreen"))

```

# Test Run 18 (Decay SOM1surf = 1.34, SOM1soil = 2, SOM2 = 0.4, Deadwood and roots * 0.001, NSlope = 0.01, DeNitrif = 0.05, NIntercept = 0.25)
# SOM1surfN * 0.25, SOM2N * 0.25
# Drainage * 0.1

```{r}
successionLog <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/LANDIS Outputs/Small Landscape/Test 18/NECN-succession-log.csv")

# Carbon
carbonDf <- successionLog %>% select(Time, SOMTC, C_SOM1surf, C_SOM1soil, C_SOM2, C_SOM3) %>% 
  pivot_longer(cols = "SOMTC":"C_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(carbonDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("SOMTC" = "red", "C_SOM1surf" = "cornflowerblue", "C_SOM1soil" = "darkorchid", "C_SOM2" = "darkorange", "C_SOM3" = "darkgreen"))

# Nitrogen
nitrogenDf <- successionLog %>% select(Time, TotalSoilN, N_SOM1surf, N_SOM1soil, N_SOM2, N_SOM3) %>% 
  pivot_longer(cols = "TotalSoilN":"N_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(nitrogenDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("TotalSoilN" = "red", "N_SOM1surf" = "cornflowerblue", "N_SOM1soil" = "darkorchid", "N_SOM2" = "darkorange", "N_SOM3" = "darkgreen"))

# Ratio
ratioDf <- rbind(carbonDf, nitrogenDf) %>%
  pivot_wider(names_from = "Pool", values_from = "g_m2") %>%
  mutate(Total = SOMTC / TotalSoilN,
         Surf = C_SOM1surf / N_SOM1surf,
         Soil = C_SOM1soil / N_SOM1soil,
         SOM2 = C_SOM2 / N_SOM2,
         SOM3 = C_SOM3 / N_SOM3) %>%
  select(Time, Total, Surf, Soil, SOM2, SOM3) %>%
  pivot_longer(cols = "Total":"SOM3", names_to = "Pool", values_to = "C:N Ratio")

ggplot(ratioDf, aes(x = Time, y = `C:N Ratio`, col = Pool)) +
  geom_line(size  = 1) +
  theme_classic() +
  ylim(0,80) +
  annotate("text", x = 31, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  # geom_hline(yintercept = 5, linetype = "dashed", col = "blue") +
  geom_hline(yintercept = 40, linetype = "dashed") +
  scale_color_manual(values = c("Total" = "red", "Surf" = "cornflowerblue", "Soil" = "darkorchid", "SOM2" = "darkorange", "SOM3" = "darkgreen"))

```


# Test Run 19 (Decay SOM1surf = 1.34, SOM1soil = 2, SOM2 = 0.4, Deadwood and roots * 0.001, NSlope = 0.01, DeNitrif = 0.05, NIntercept = 0.25)
# SOM1surfN * 0.1, SOM2N * 0.25
# Drainage * 0.1

```{r}
successionLog <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/LANDIS Outputs/Small Landscape/Test 19/NECN-succession-log.csv")

# Carbon
carbonDf <- successionLog %>% select(Time, SOMTC, C_SOM1surf, C_SOM1soil, C_SOM2, C_SOM3) %>% 
  pivot_longer(cols = "SOMTC":"C_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(carbonDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("SOMTC" = "red", "C_SOM1surf" = "cornflowerblue", "C_SOM1soil" = "darkorchid", "C_SOM2" = "darkorange", "C_SOM3" = "darkgreen"))

# Nitrogen
nitrogenDf <- successionLog %>% select(Time, TotalSoilN, N_SOM1surf, N_SOM1soil, N_SOM2, N_SOM3) %>% 
  pivot_longer(cols = "TotalSoilN":"N_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(nitrogenDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("TotalSoilN" = "red", "N_SOM1surf" = "cornflowerblue", "N_SOM1soil" = "darkorchid", "N_SOM2" = "darkorange", "N_SOM3" = "darkgreen"))

# Ratio
ratioDf <- rbind(carbonDf, nitrogenDf) %>%
  pivot_wider(names_from = "Pool", values_from = "g_m2") %>%
  mutate(Total = SOMTC / TotalSoilN,
         Surf = C_SOM1surf / N_SOM1surf,
         Soil = C_SOM1soil / N_SOM1soil,
         SOM2 = C_SOM2 / N_SOM2,
         SOM3 = C_SOM3 / N_SOM3) %>%
  select(Time, Total, Surf, Soil, SOM2, SOM3) %>%
  pivot_longer(cols = "Total":"SOM3", names_to = "Pool", values_to = "C:N Ratio")

ggplot(ratioDf, aes(x = Time, y = `C:N Ratio`, col = Pool)) +
  geom_line(size  = 1) +
  theme_classic() +
  ylim(0,80) +
  annotate("text", x = 31, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  # geom_hline(yintercept = 5, linetype = "dashed", col = "blue") +
  geom_hline(yintercept = 40, linetype = "dashed") +
  scale_color_manual(values = c("Total" = "red", "Surf" = "cornflowerblue", "Soil" = "darkorchid", "SOM2" = "darkorange", "SOM3" = "darkgreen"))

```

# Test Run 20 (Decay SOM1surf = 1.34, SOM1soil = 2, SOM2 = 0.4, Deadwood and roots * 0.001, NSlope = 0.01, DeNitrif = 0.05, NIntercept = 0.25)
# SOM1surfN * 0.1, SOM2N * 0.25, SOM1soilN * 0.1
# Drainage * 0.1

```{r}
successionLog <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/LANDIS Outputs/Small Landscape/Test 20/NECN-succession-log.csv")

# Carbon
carbonDf <- successionLog %>% select(Time, SOMTC, C_SOM1surf, C_SOM1soil, C_SOM2, C_SOM3) %>% 
  pivot_longer(cols = "SOMTC":"C_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(carbonDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("SOMTC" = "red", "C_SOM1surf" = "cornflowerblue", "C_SOM1soil" = "darkorchid", "C_SOM2" = "darkorange", "C_SOM3" = "darkgreen"))

# Nitrogen
nitrogenDf <- successionLog %>% select(Time, TotalSoilN, N_SOM1surf, N_SOM1soil, N_SOM2, N_SOM3) %>% 
  pivot_longer(cols = "TotalSoilN":"N_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(nitrogenDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("TotalSoilN" = "red", "N_SOM1surf" = "cornflowerblue", "N_SOM1soil" = "darkorchid", "N_SOM2" = "darkorange", "N_SOM3" = "darkgreen"))

# Ratio
ratioDf <- rbind(carbonDf, nitrogenDf) %>%
  pivot_wider(names_from = "Pool", values_from = "g_m2") %>%
  mutate(Total = SOMTC / TotalSoilN,
         Surf = C_SOM1surf / N_SOM1surf,
         Soil = C_SOM1soil / N_SOM1soil,
         SOM2 = C_SOM2 / N_SOM2,
         SOM3 = C_SOM3 / N_SOM3) %>%
  select(Time, Total, Surf, Soil, SOM2, SOM3) %>%
  pivot_longer(cols = "Total":"SOM3", names_to = "Pool", values_to = "C:N Ratio")

ggplot(ratioDf, aes(x = Time, y = `C:N Ratio`, col = Pool)) +
  geom_line(size  = 1) +
  theme_classic() +
  ylim(0,80) +
  annotate("text", x = 31, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  # geom_hline(yintercept = 5, linetype = "dashed", col = "blue") +
  geom_hline(yintercept = 40, linetype = "dashed") +
  scale_color_manual(values = c("Total" = "red", "Surf" = "cornflowerblue", "Soil" = "darkorchid", "SOM2" = "darkorange", "SOM3" = "darkgreen"))
```







# LAI stuff

```{r}
# LAI
input_directory <- "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/LANDIS Outputs/Small Landscape/Test 14/LAI"
LAI_files <- list.files(input_directory, pattern = "\\.img$", full.names = TRUE)
LAI <- list()
for (i in input_directory) {
  LAI[[i]] <- rast(LAI_files)
}

plot(LAI[[1]][[1]])
plot(LAI[[1]][[3]])
plot(LAI[[1]][[4]])
plot(LAI[[1]][[5]])
plot(LAI[[1]][[6]])
plot(LAI[[1]][[7]])
plot(LAI[[1]][[8]])
plot(LAI[[1]][[9]])
plot(LAI[[1]][[10]])
plot(LAI[[1]][[2]])

LAI1 <- LAI[[1]][[1]] %>% as.data.frame() %>% filter(Layer_1 > 0) %>% `colnames<-`(1) 
LAI2 <- LAI[[1]][[3]] %>% as.data.frame() %>% filter(Layer_1 > 0) %>% `colnames<-`(2) 
LAI3 <- LAI[[1]][[4]] %>% as.data.frame() %>% filter(Layer_1 > 0) %>% `colnames<-`(3) 
LAI4 <- LAI[[1]][[5]] %>% as.data.frame() %>% filter(Layer_1 > 0) %>% `colnames<-`(4) 
LAI5 <- LAI[[1]][[6]] %>% as.data.frame() %>% filter(Layer_1 > 0) %>% `colnames<-`(5) 
LAI6 <- LAI[[1]][[7]] %>% as.data.frame() %>% filter(Layer_1 > 0) %>% `colnames<-`(6) 
LAI7 <- LAI[[1]][[8]] %>% as.data.frame() %>% filter(Layer_1 > 0) %>% `colnames<-`(7) 
LAI8 <- LAI[[1]][[9]] %>% as.data.frame() %>% filter(Layer_1 > 0) %>% `colnames<-`(8) 
LAI9 <- LAI[[1]][[10]] %>% as.data.frame() %>% filter(Layer_1 > 0) %>% `colnames<-`(9)
LAI10 <- LAI[[1]][[2]] %>% as.data.frame() %>% filter(Layer_1 > 0) %>% `colnames<-`(10)


max_rows <- max(nrow(LAI1),nrow(LAI2),nrow(LAI3),nrow(LAI4),nrow(LAI5),nrow(LAI6),nrow(LAI7),nrow(LAI8),nrow(LAI9),nrow(LAI10))

LAI1 <- pad_with_na(LAI1, max_rows)
LAI2 <- pad_with_na(LAI2, max_rows)
LAI3 <- pad_with_na(LAI3, max_rows)
LAI4 <- pad_with_na(LAI4, max_rows)
LAI5 <- pad_with_na(LAI5, max_rows)
LAI6 <- pad_with_na(LAI6, max_rows)
LAI7 <- pad_with_na(LAI7, max_rows)
LAI8 <- pad_with_na(LAI8, max_rows)
LAI9 <- pad_with_na(LAI9, max_rows)
LAI10 <- pad_with_na(LAI10, max_rows)

LAIbox <- cbind(LAI1,LAI2,LAI3,LAI4,LAI5,LAI6,LAI7,LAI8,LAI9,LAI10)

LAIbox <- LAIbox %>%
  pivot_longer(cols = 1:10, names_to = "LAI", values_to = "value")
LAIbox$LAI <- factor(LAIbox$LAI, levels = 1:10)

ggplot(LAIbox, aes(x = LAI, y = value)) +
  geom_boxplot() +
  theme_classic()


```


```{r}
successionLog <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/LANDIS Outputs/Small Landscape/FAKE/NECN-succession-log.csv")

# Carbon
carbonDf <- successionLog %>% select(Time, SOMTC, C_SOM1surf, C_SOM1soil, C_SOM2, C_SOM3) %>% 
  pivot_longer(cols = "SOMTC":"C_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(carbonDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("SOMTC" = "red", "C_SOM1surf" = "cornflowerblue", "C_SOM1soil" = "darkorchid", "C_SOM2" = "darkorange", "C_SOM3" = "darkgreen"))

# Nitrogen
nitrogenDf <- successionLog %>% select(Time, TotalSoilN, N_SOM1surf, N_SOM1soil, N_SOM2, N_SOM3) %>% 
  pivot_longer(cols = "TotalSoilN":"N_SOM3", names_to = "Pool", values_to = "g_m2")
ggplot(nitrogenDf, aes(x = Time, y = g_m2, col = Pool)) +
  geom_line(size = 1) +
  theme_classic() +
  annotate("text", x = 27, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  scale_color_manual(values = c("TotalSoilN" = "red", "N_SOM1surf" = "cornflowerblue", "N_SOM1soil" = "darkorchid", "N_SOM2" = "darkorange", "N_SOM3" = "darkgreen"))

# Ratio
ratioDf <- rbind(carbonDf, nitrogenDf) %>%
  pivot_wider(names_from = "Pool", values_from = "g_m2") %>%
  mutate(Total = SOMTC / TotalSoilN,
         Surf = C_SOM1surf / N_SOM1surf,
         Soil = C_SOM1soil / N_SOM1soil,
         SOM2 = C_SOM2 / N_SOM2,
         SOM3 = C_SOM3 / N_SOM3) %>%
  select(Time, Total, Surf, Soil, SOM2, SOM3) %>%
  pivot_longer(cols = "Total":"SOM3", names_to = "Pool", values_to = "C:N Ratio")

ggplot(ratioDf, aes(x = Time, y = `C:N Ratio`, col = Pool)) +
  geom_line(size  = 1) +
  theme_classic() +
  ylim(0,80) +
  annotate("text", x = 31, y = Inf, label = "DecaySurf = 1.34\nDecaySoil = 2\nDecaySOM2 = 0.4\nDecaySOM3 = 0.0000001\nDenitrification = 0.05\nNSlope = 0.01\nNIntercept = 0.25", 
           hjust = 1, vjust = 1, size = 3, color = "black", 
           fontface = "bold", family = "serif") +
  theme(plot.margin = margin(10, 40, 10, 10)) +
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0,100)) +
  geom_hline(yintercept = 5, linetype = "dashed", col = "blue") +
  geom_hline(yintercept = 10, linetype = "dashed") +
  scale_color_manual(values = c("Total" = "red", "Surf" = "cornflowerblue", "Soil" = "darkorchid", "SOM2" = "darkorange", "SOM3" = "darkgreen"))

```

# For writing new rasters out

```{r}
SOM1surfN <- rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/Small Landscape/Clipped Piedmont/SOM1surfN.tif")
SOM1soilN <- rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/Small Landscape/Clipped Piedmont/SOM1soilN.tif")
plot(SOM1surfN)
plot(SOM2N)

values(SOM1surfN) <- values(SOM1surfN) * 0.1
values(SOM1soilN) <- values(SOM1soilN) * 0.25


writeRaster(SOM1surfN,
            filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/Small Landscape/Test Rasters/SOM1soilN_0.25.tif",
            datatype = "FLT4S",
            NAflag = 1.01,
            overwrite = TRUE)


```


soildrainage <- rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/Small Landscape/Clipped Piedmont/Drainage.tif")
plot(soildrainage)

values(soildrainage) <- values(soildrainage) * 0.1

writeRaster(soildrainage,
            filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/Small Landscape/Test Rasters/Drainage_0.1.tif",
            datatype = "FLT4S",
            NAflag = 0.01,
            overwrite = TRUE)



values(soildrainage) <- values(soildrainage) %>% as.data.frame() %>% mutate(Drainage = ifelse(Drainage < 0.4, Drainage *2, Drainage)) %>% as.matrix()

plot(soildrainage)
soildrainage2 <- rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/Small Landscape/Clipped Piedmont/Drainage.tif")
plot(soildrainage2)
```





```{r}
managementAreasRast <- rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/Small Landscape/Harvest/fakeOwnership.tif")
standsRast <- rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/Small Landscape/Harvest/smallStandsRast.tif")

plot(managementAreasRast)
plot(standsRast)

dataTRY <- data.table::fread("C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/Small Landscape/dataTRY.txt")
```







